\begin{biblio}

\bibitem{Grune}
Grune, L. Nonlinear model predictive control / L. Grune, J. Pannek // Springer London. -- 2011.

\bibitem{Mayne}
Rawlings, J.B. Model Predictive Control: Theory and Design / J.B.~Rawlings, D.Q.~Mayne // Madison: Nob Hill Publishing. -- 2009.

\bibitem{QuinBadgwell}
Badgwell, T.A. Model-Predictive Control in Practice / T.A. Badgwell, S.J. Qin //  Encyclopedia of Systems and Control. Springer, London. -- 2015.

\bibitem{ChenAlgower}
Chen, H. A Quasi-Infinite Horizon Nonlinear Model Predictive Control Scheme with Guaranteed Stability /  H.~Chen,  F.~Allgower  //
Automatica. -- 1998. -- Vol.~34, No.~10. -- P.~1205-1217.

\bibitem{FernandoFontes}
Fontes, F.A.C.C. A General Framework to Design Stabilizing Nonlinear Model Predictive Controllers / F.A.C.C.~Fontes // Systems \& Control letters. -- 2000. -- Vol. 42, No. 2. --  P.~127-143.

\bibitem{Bemporad}
Bemporad, A. The explicit linear quadratic regulator for constrained systems / A. Bemporad et al. // Automatica. -- 2002. -- Vol. 38, No. 1. -- P.~3-20.

\bibitem{Domahidi}
Domahidi, A. Learning a feasible and stabilizing explicit model predictive control law by robust optimization / A. Domahidi et al. // Proceedings of the IEEE Conference on Decision \& Control. -- 2011. -- No.~EPFL-CONF-169723.

\bibitem{Chakrabarty}
Chakrabarty, A. Support Vector Machine Informed Explicit Nonlinear Model Predictive Control Using Low-Discrepancy Sequences / A. Chakrabarty et al. // IEEE Transactions on Automatic Control. -- 2017. -- Vol. 62, No. 1. -- P. 135-148.

\bibitem{Johansen}
Johansen, T. A. Approximate explicit receding horizon control of constrained nonlinear systems // Automatica.  -- 2004. -- Vol. 40, No. 2. -- P.~293-300.

\bibitem{ParisiniZoppoli}
Parisini, T. A receding-horizon regulator for nonlinear systems and a neural approximation / T. Parisini, R. Zoppoli // Automatica. -- 1995. -- Vol.~31, No.~10. -- P. 1443-1451.

\bibitem{ParisiniSanquineti}
Parisini, T. Nonlinear stabilization by receding-horizon neural regulators / T. Parisini, M. Sanquineti, R. Zoppoli // International Journal of Control. -- 1998. -- Vol. 70,No. 3. -- P. 341-362.

\bibitem{Akesson}
Akesson, B. M. A neural network model predictive controller /B.M. Akesson, H.T. Toivonen // Journal of Process Control. -- 2006. -- Vol.~16, No.~9. -- P. 937-946.

\bibitem{Pin}
Pin, G. Approximate model predictive control laws for constrained nonlinear discrete-time systems: analysis and offline design / G. Pin et al. // International Journal of Control. -- 2013. -- Vol.86, No.5. -- P. 804-820.

\bibitem{Aswani}
Aswani, A. Provably safe and robust learning-based model predictive control / A. Aswani et al. // Automatica. -- 2013. -- Vol. 49, No. 5. -- P. 1216-1226.

\bibitem{Rosolia}
Rosolia, U. Learning model predictive control for iterative tasks. a data-driven control framework / U.Rosolia, F. Borrelli // IEEE Transactions on Automatic Control. -- 2018. -- Vol. 63, No. 7.

\bibitem{Goodfellow}
Goodfellow, I. Deep learning / I.Goodfellow et al. // Cambridge : MIT press. -- 2016. -- Vol. 1.

\bibitem{Csaji}
Csaji, B. C. Approximation with artificial neural networks // Faculty of Sciences, Etvs Lornd University, Hungary. -- 2001. -- Vol. 24. -- P. 48.

\bibitem{CasADi}
Andersson, J.A.E. CasADi: a software framework for nonlinear optimization and optimal control / J.A.E. Andersson  et al. // Mathematical Programming Computation. -- 2018. -- P. 1-36.

\bibitem{Diehl}
Diehl, M. Efficient numerical methods for nonlinear MPC and moving horizon estimation /M. Diehl, H. J. Ferreau, N. Haverbeke // Nonlinear model predictive control. Springer, Berlin, Heidelberg. -- 2009. -- P. 391-417.

\bibitem{HertnerKohler}
Hertneck, M. Learning an approximate model predictive controller with guarantees / M.Hertneck et al. // IEEE Control Systems Letters. -- 2018. -- Vol. 2. No. 3. -- P. 543-548.

\bibitem{Halton}
Kocis, L. Computational investigations of low-discrepancy sequences / L. Kocis, W.J. Whiten // ACM Transactions on Mathematical Software (TOMS). -- 1997. -- No. 23. Vol. 2. -- P. 266-294.

\bibitem{SVM}
Cristianini, N. An introduction to support vector machines and other kernel-based learning methods // Cambridge university press. -- 2000.

\bibitem{Pendulum}
Liberzon, D. Switching in systems and control // Springer Science and Business Media. -- 2003.

\bibitem{Pavlovets}
Павловец, М.Е. Применение методов машинного
обучения в системах управления по прогнозирующей
модели / М.Е. Павловец, Н.М. Дмитрук // XIX Международная научная конференция по дифференциальным
уравнениям "Еругинские чтения-2019": материалы международной научной
конференции. Могилев, 14-17 мая 2019 г. -- С. 127-129.

\end{biblio} 