\begin{biblio}

\bibitem{Grune}
Grune L., Pannek J. Nonlinear model predictive control. -- Springer London, 2011.

\bibitem{Mayne}
Rawlings, J.B. Model Predictive Control: Theory and Design / J.B. Rawlings, D.Q.~Mayne. -- Madison:
Nob Hill Publishing, 2009. -- 576 p.

\bibitem{QuinBadgwell}
Badgwell T.A., Qin S.J. (2015) Model-Predictive Control in Practice. In: Baillieul J., Samad T. (eds) Encyclopedia of Systems and Control. Springer, London

\bibitem{ChenAlgower}
H.Chen, F.Allgower A Quasi-Infinite Horizon Nonlinear Model Predictive Control Scheme with Guaranteed Stability /  H.~Chen,  F.~Allgower  //
Automatica. -- 1998. -- Vol.~34, no.~10. -- P.~1205-1217.

\bibitem{FernandoFontes}
Fernando A.C.C. Fontes A General Framework to Design Stabilizing Nonlinear Model Predictive Controllers / F. A.C.C.~Fontes // Systems \& Control letters.  -- 2000.  P.~1-13.

\bibitem{Bemporad}
Bemporad A. et al. The explicit linear quadratic regulator for constrained systems //Automatica. - 2002. - T. 38. - N$\textsuperscript{\underline{o}}$ . 1. - C. 3-20.

\bibitem{Domahidi}
Domahidi A. et al. Learning a feasible and stabilizing explicit model predictive control law by robust optimization //Proceedings of the IEEE Conference on Decision \& Control. - 2011. - N$\textsuperscript{\underline{o}}$. EPFL-CONF-169723.

\bibitem{Chakrabarty}
Chakrabarty A. et al. Support Vector Machine Informed Explicit Nonlinear Model Predictive Control Using Low-Discrepancy Sequences //IEEE Trans. Automat. Contr. - 2017. - T. 62. - N$\textsuperscript{\underline{o}}$. 1. - C. 135-148.

\bibitem{Johansen}
Johansen T. A. Approximate explicit receding horizon control of constrained nonlinear systems //Automatica.  - 2004. - T.40. - N$\textsuperscript{\underline{o}}$. 2. - C. 293-300.

\bibitem{ParisiniZoppoli}
Parisini T., Zoppoli R. A receding-horizon regulator for nonlinear systems and a neural approximation //Automatica. - 1995. -T. 31. - N$\textsuperscript{\underline{o}}$.10, - C. 1443-1451.

\bibitem{ParisiniSanquineti}
Parisini T., Sanguineti M., Zoppoli R. Nonlinear stabilization by receding-horizon neural regulators //International Journal of Control. - 1998. - T. 70. - N$\textsuperscript{\underline{o}}$ 3. - C. 341-362.

\bibitem{Akesson}
Akesson B. M., Toivonen H. T. A neural network model predictive controller //Journal of Process Control. - 2006. - T.16. - N$\textsuperscript{\underline{o}}$. 9. - C. 937-946.

\bibitem{Pin}
Pin G. et al. Approximate model predictive control laws for constrained nonlinear discrete-time systems: analysis and offline design //International Journal of Control. - 2013. - T.86. - N$\textsuperscript{\underline{o}}$.5. - C. 804-820.

\bibitem{Aswani}
Aswani A. et al. Provably safe and robust learning-based model predictive control //Automatica. - 2013. - T. 49. - N$\textsuperscript{\underline{o}}$.5. - C. 1216-1226.

\bibitem{Rosolia}
Rosolia U., Borrelli F. Learning model predictive control for iterative tasks. a data-driven control framework //IEEE Transactions on Automatic Control. - 2018. - T. 63. -N$\textsuperscript{\underline{o}}$.7.

\bibitem{Goodfellow}
Goodfellow I. et al. Deep learning. - Cambridge : MIT press, 2016. - T.1.

\bibitem{Csaji}
Csaji B. C. Approximation with artificial neural networks //Faculty of Sciences, Etvs Lornd University, Hungary. - 2001. - T. 24. - C.48.

\bibitem{CasADi} 
CasADi: a software framework for nonlinear optimization and optimal control / J.A.E. Andersson  et al. // Mathematical Programming Computation. -- 2018. -- P. 1-36.

\bibitem{Diehl} 
Diehl M., Ferreau H. J., Haverbeke N. Efficient numerical methods for nonlinear MPC and moving horizon estimation // Nonlinear model predictive control. -- Springer, Berlin, Heidelberg, 2009. -- P. 391-417.

\bibitem{HertnerKohler}
Hertneck M. et al. Learning an approximate model predictive controller with guarantees //IEEE Control Systems Letters. - 2018. - T. 2. - N$\textsuperscript{\underline{o}}$. 3. - C. 543-548.

\end{biblio} 